A thesis draft

### 2018-11-16 res/sections/08-Background.tex
Grammar
Co-Authored-By: mzanella <mzanella@users.noreply.github.com>

\emph{SDN controllers}, are logically centralized components that
receive requests from the mentioned SDN applications and either translate them 
in a fashion that can be understood from the lower layer\todo{who?}, or collect 
data needed by the application itself. 
Due to the variety of tasks a controller has to accomplish, its logical 
suddivision is achieved with a three-layer architecture, in which every layer 
exposes it's own interface, that can be consequently used by the upper 
layers, up to the \emph{NBI agents}.
NBI agents manages the communication with SDN applications, exposing interfaces
that usually provide an abstract view of the network and a set of
the controller functionalities.
In particular, the middle layer represents the controller inner-logic, which 
process the requests coming from the upper layer (aka the third layer), that 
has the specific task to communicate with the remaining network compoents, in 
other words the Control to Data-Plane Interface and/or the already 
mentioned southbound interface.

>>>>

\emph{SDN controllers}, are logically centralized components that
receive requests from the mentioned SDN applications and either translate them 
in a fashion that can be understood from the lower layer\todo{who?}, or collect 
data needed by the application itself. 
Due to the variety of tasks a controller has to accomplish, its logical 
suddivision is achieved with a three-layer architecture, in which every layer 
exposes it's own interface, that can be consequently used by the upper 
layers, up to the \emph{NBI agents}.
NBI agent manages the communications with SDN applications, exposing interfaces
that usually provide an abstract view of the network and a set of
the controller functionalities.
In particular, the middle layer represents the controller inner-logic, which 
process the requests coming from the upper layer (aka the third layer), that 
has the specific task to communicate with the remaining network compoents, in 
other words the Control to Data-Plane Interface and/or the already 
mentioned southbound interface.
